Experiment 3

### 2021-07-17 experiments/experiment 1/experiment 1.Rmd
correct colour order issue

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  html_document:
    keep_md: yes
---

@@

```{r}
var_expt <- create_diversity()
```

@@

```{r}
options(mc.cores = 4)
```

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data.RDS"))

@@

>>>>

---
title: "Experiment 1"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

```{r}
var_expt <- create_diversity()

var_expt[["pars"]][[20]]$CB
var_expt[["pars"]][[20]]$SB
var_expt[["pars"]][[20]]$PB

@@

```{r}
options(mc.cores = 12)
```

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 1/data/ss_data_latest.RDS"))

@@

```{r}
var_expt <- readRDS(here("experiments/experiment 1/data/ss_data_latest.RDS"))

@@

## negative abundance investigation

var_expt$pars[[1]]
dd <- var_expt$ss_res[[1]]
dd1 <- filter(dd, PB_1<(-0.0001))
dd1$a_O

a_Os <- a_Os[355]
ss_expt <- expand.grid(N_CB = initial_CBs,
                      N_PB = initial_PBs,
                      N_SB = initial_SBs,
                      a_O = a_Os)

var_expt_master <- var_expt
var_expt <- var_expt[1,]
var_expt_test <- run_ss_var_experiment()
res <- var_expt_test$ss_res[[1]]
#saveRDS(var_expt, here("experiments/experiment 1/data/ss_data.RDS"))

sim_number <- 1
log10_a <- log10(a_Os[355]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[354]) ## very slowly goes anoxic
#log10_a <- log10(a_Os[356]) ## very very very  slowly goes anoxic
#log10_a <- log10(a_Os[357]) ## does not go anoxic

default_log10a_series <- c(log10_a, log10_a)
initial_state <- new_initial_state(num_CB_strains,
                                   num_PB_strains,
                                   num_SB_strains,
                                   values = "bush_ssfig3")
initial_state[grep("CB_", names(initial_state))] <- 10^10/num_CB_strains
sim_res_novar <- run_simulation(parameter_values = var_expt$pars[[sim_number]],
                          initial_state = initial_state)
plot_dynamics(sim_res_novar)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)

### 2021-07-17 experiments/experiment 3/experiment 3.Rmd
correct colour order issue

---
title: "Experiment 3"
author: "Owen Petchey"
date: "6/25/2021"
output:
  html_document:
    keep_md: yes
---

@@

```{r}
var_expt <- run_ss_var_experiment()
saveRDS(var_expt, here("experiments/experiment 3/data/ss_data.RDS"))

>>>>

---
title: "Experiment 3"
author: "Owen Petchey"
date: "6/25/2021"
output:
  pdf_document: default
  html_document:
    keep_md: yes
---

@@

```{r}
#var_expt <- run_ss_var_experiment()
#saveRDS(var_expt, here("experiments/experiment 3/data/ss_data.RDS"))
